---
title: "assignment04.Rmd"
author: "Tongxin Zhu"
date: "2/27/2020"
output: html_document

---
```{r set up}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(quiet = TRUE)
```


1. Data Loading & Cleaning
```{r}
library(readr)
library(stringr)
library(tidyverse)
Crimes_reduced <- read_csv("data/Crimes-reduced.csv",
                           col_types = cols(Latitude = col_character(), 
                                            Longitude = col_character()))

View(Crimes_reduced)

names(Crimes_reduced) <- str_replace_all(names(Crimes_reduced), c(" "="_"))
names(Crimes_reduced) <- str_to_lower(names(Crimes_reduced))
```
I would expect the same error because x_coordinate, y_coordinate and location variables are regarded as logical variables by system default, which means they can only take the value of "True/False" but not numeric values. Therefore, when they showed numeric values, it appeared as errors.


2. Filtering the data to homicides within ten years of today
```{r}
library(lubridate)
crime_reduced <- Crimes_reduced %>% filter(longitude!="NA", latitude !="NA")

homicides <- crime_reduced %>% filter(primary_type == "HOMICIDE")

homicides$date = as.Date.character(homicides$date, format = c("%m/%d/%Y"))

crimes_lim <- homicides %>%
  filter(date >= "2010-02-25")

table(year(crimes_lim$date))

min(crimes_lim$date)
```


3. Convert Lat/Lon to Points Geometry
```{r}
library(sf)
crimes_lim <- st_as_sf(
  crimes_lim,
  coords = c("longitude", "latitude"),
  crs = 4326)

glimpse(crimes_lim)

class(crimes_lim)

ggplot(crimes_lim)+
  geom_sf(aes(color=arrest), alpha=0.2)
```


4. Load Census Tracts, Perform a Spatial Join, and Create Choropleth
```{r}
library(sf)
library(gridExtra)
chicago_gdf <- st_read("data/Boundaries - Census Tracts - 2010/geo_export_256823b2-3748-42c1-a544-7329a725afb5.shp") %>%
  select(geoid10, geometry)

chicago_gdf <- st_set_crs(chicago_gdf, 4326)
chicago_merged <- st_join(chicago_gdf, crimes_lim)

chicago_merged_agg <-chicago_merged %>%
  group_by(geoid10) %>%
  summarise(arrest_tot=sum(arrest), count=length(arrest)) %>%
  mutate(arrest_rate=arrest_tot/count)
chicago_merged_agg <- na.omit(chicago_merged_agg)

ggplot(chicago_merged_agg)+
  geom_sf(aes(fill=count, alpha=arrest_rate, color=count))+
  theme_void()
```
5. Using the Census API to retrieve household income, educational attainment,
and poverty status for all of the Census tracts in Cook County, Illinois
```{r api key}
library(tidycensus)
credential <- read_file("credentials.txt")
census_api_key(credential, install = TRUE, overwrite = TRUE)
```

```{r retrieve census data with tidycensus}
acs5 <- load_variables(2017, "acs5")

cook13_17 <- get_acs(geography = "tract", 
                     variables = c("B19001_001E", "B15003_001E", "B99172_001E"),
                     state = "17", county = "031", year = 2017, output = "wide")
```

```{r Using URL to retrieve the same data}
library(httr)
library(jsonlite)
credential <- read_file("credentials.txt")
url <- "https://api.census.gov/data/2017/acs/acs5?get=NAME,B19001_001E,B15003_001E,B99172_001E&for=tract:*&in=state:17&in=county:031&key=90e7f8de0a44ee8d3576184aa7212a46334b848b"

cook_json <- GET(url = url,
                        user_agent("Georgetown Univ. Student Data Collector (tz163@georgetown.edu)"))

http_status(cook_json)
cook_json <- content(cook_json, as = "text")

cook_matrix <- fromJSON(cook_json)
cook_data <- as.tibble(cook_matrix[2:nrow(cook_matrix),],
                       .name_repair = "minimal")
names(cook_data) <- cook_matrix[1, ]

check_tidy <- select(cook13_17, 3,5,7)
check_url <- select(cook_data, 2:4)
check_url$B19001_001E <- as.numeric(check_url$B19001_001E)
check_url$B15003_001E <- as.numeric(check_url$B15003_001E)
check_url$B99172_001E <- as.numeric(check_url$B99172_001E)
all.equal(check_tidy, check_url)

```


6. Writing an R Function to Query the Census API and Create a Map
```{r, results = "hide"}
get_api <- function(cen_year=2017, cen_state="IL", cen_county="Cook", cen_inc="B19001_001E") {
  
censusapi <- get_acs(state = cen_state,
                     county = cen_county,
                     year = cen_year,
                     variables = c(income = cen_inc),
                     geography = "county", geometry = TRUE)
  
  map <- ggplot(censusapi)+
  geom_sf()
return(map)
}

get_api(2017, "17", "31", "B19001_001E")
```